---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

```{css}
body {background-color: #FCF7F8}
h2 {color: #804000; background-color: white; text-align: center; padding: 20px}
h3 {text-align: center}
p {text-align: center}
```

```{r}
logged_data <- read_csv(
  "https://docs.google.com/spreadsheets/d/e/2PACX-1vRg7nFZ1M_DERzhhya2edsEYDaRXLaf77V2Oo1NbdVUw5BZSlwxv7qCOl2fcMXb0s9Lwu_kSEuNHKuU/pub?gid=996593738&single=true&output=csv"
) %>% rename(morning_or_afternoon = 2,
             temperature = 3, 
             drink_type = 4,
             hot_or_iced = 5, 
             coffee_type = 6, 
             tea_type = 7) 

latest_data <- logged_data %>%
  mutate(temp_factor = case_when(
    temperature < 10 ~ "< 10",
    temperature < 12 ~ "10-12",
    temperature < 14 ~ "12-14",
    temperature < 16 ~ "14-16",
    temperature < 18 ~ "16-18",
    temperature < 20 ~ "18-20",
    temperature < 22 ~ "20-22",
    temperature < 24 ~ "22-24",
    temperature < 26 ~ "24-26",
    temperature < 28 ~ "26-28",
    temperature < 30 ~ "28-30",
    TRUE ~ "> 30"))
```

## Overall summary of what our customers have ordered, categorised by the temperature!

```{r}
latest_data %>%
  ggplot() + 
  geom_bar((aes(y = temp_factor,
                fill = drink_type))) +
  scale_fill_brewer(palette = "PuOr") + 
  labs(y = "Temperature (in degrees Celsius)",
       fill = "Drink Type")
```

## Does the temperature influence whether our customers get hot or iced drinks?

```{r}
latest_data %>%
  ggplot() + 
  geom_bar((aes(y = temp_factor,
                fill = hot_or_iced))) + 
  theme_bw() +
  labs(y = "Temperature (in degrees Celsius)", 
       fill = "Hot or Iced")
```

```{r}
temp_over_20 <- latest_data$temperature >= 20
temp_not_over_20 <- latest_data$temperature < 20

over_20 <- length(latest_data$hot_or_iced[temp_over_20])
under_20 <- length(latest_data$hot_or_iced[temp_not_over_20])

hot_drinks_over_20 <- sum(latest_data$hot_or_iced[temp_over_20] == "Hot")
iced_drinks_over_20 <- sum(latest_data$hot_or_iced[temp_over_20] == "Iced")

prop_hot_drinks_over_20 <- round(hot_drinks_over_20/over_20, 2) * 100
prop_iced_drinks_over_20 <- round(iced_drinks_over_20/over_20, 2) * 100

hot_drinks_under_20 <- sum(latest_data$hot_or_iced[temp_not_over_20] == "Hot")
iced_drinks_under_20 <- sum(latest_data$hot_or_iced[temp_not_over_20] == "Iced")

prop_hot_drinks_under_20 <- round(hot_drinks_under_20/under_20, 2) * 100
prop_iced_drinks_under_20 <- round(iced_drinks_under_20/under_20, 2) * 100
```

This graph tracks the number of customers who get hot drinks or iced drinks, grouped by the outside temperature of when the customer ordered the drink.

When the temperature is **under** 20 degrees Celsius, `r prop_iced_drinks_under_20`% of customers order iced drinks and `r prop_hot_drinks_under_20`% of customers order hot drinks.

When the temperature **is/over** 20 degrees Celsius, `r prop_iced_drinks_over_20`% of customers order iced drinks and `r prop_hot_drinks_over_20`% of customers order hot drinks.

## Does the period of day impact customers choices of teas?

### "Other" indicates that the customer did not order a tea.

```{r}
non_tea_orders <- is.na(latest_data$tea_type)
latest_data$tea_type[non_tea_orders] <- "Other"

latest_data %>%
  ggplot() +
  geom_bar(aes(y = tea_type,
               fill = morning_or_afternoon)) +
  theme_bw() +
  labs(y = "Tea Type", 
       fill = "Morning or Afternoon")
```

```{r}
cumulative <- as.numeric(latest_data$tea_type %>% length())
other_orders <- as.numeric(sum(latest_data$tea_type == "Other"))
tea_orders <- cumulative - other_orders

traditional_black <- as.numeric(sum(latest_data$tea_type == "Traditional Black"))
flavoured_black <- as.numeric(sum(latest_data$tea_type == "Flavoured Black"))
earl_grey <- as.numeric(sum(latest_data$tea_type == "Earl Grey"))
traditional_green <- as.numeric(sum(latest_data$tea_type == "Traditional Green"))
flavoured_green <- as.numeric(sum(latest_data$tea_type == "Flavoured Green"))
herbal <- as.numeric(sum(latest_data$tea_type == "Herbal"))
fruit <- as.numeric(sum(latest_data$tea_type == "Fruit"))
white <- as.numeric(sum(latest_data$tea_type == "White"))
oolong <- as.numeric(sum(latest_data$tea_type == "Oolong"))
organic <- as.numeric(sum(latest_data$tea_type == "Organic"))
decaf <- as.numeric(sum(latest_data$tea_type == "Decaffeinated"))
artisan <- as.numeric(sum(latest_data$tea_type == "Artisan"))
```

```{r}
black <- latest_data$tea_type == "Traditional Black" 
morning_black <- sum(latest_data$morning_or_afternoon[black] == "Morning")
afternoon_black <- sum(latest_data$morning_or_afternoon[black] == "Afternoon")

black2 <- latest_data$tea_type == "Flavoured Black" 
morning_black2 <- sum(latest_data$morning_or_afternoon[black2] == "Morning")
afternoon_black2 <- sum(latest_data$morning_or_afternoon[black2] == "Afternoon")

earl_grey2 <- latest_data$tea_type == "Earl Grey"
morning_earl_grey2 <- sum(latest_data$morning_or_afternoon[earl_grey2] == "Morning")
afternoon_earl_grey2 <- sum(latest_data$morning_or_afternoon[earl_grey2] == "Afternoon")

green <- latest_data$tea_type == "Traditional Green"
morning_green <- sum(latest_data$morning_or_afternoon[green] == "Morning")
afternoon_green <- sum(latest_data$morning_or_afternoon[green] == "Afternoon")

green2 <- latest_data$tea_type == "Flavoured Green"
morning_green2 <- sum(latest_data$morning_or_afternoon[green2] == "Morning")
afternoon_green2 <- sum(latest_data$morning_or_afternoon[green2] == "Afternoon")

herbal_2 <- latest_data$tea_type == "Herbal"
morning_herbal <- sum(latest_data$morning_or_afternoon[herbal_2] == "Morning")
afternoon_herbal <- sum(latest_data$morning_or_afternoon[herbal_2] == "Afternoon")

fruit_2 <- latest_data$tea_type == "Fruit"
morning_fruit <- sum(latest_data$morning_or_afternoon[fruit_2] == "Morning")
afternoon_fruit <- sum(latest_data$morning_or_afternoon[fruit_2] == "Afternoon")

white_2 <- latest_data$tea_type == "White"
morning_white <- sum(latest_data$morning_or_afternoon[white_2] == "Morning")
afternoon_white <- sum(latest_data$morning_or_afternoon[white_2] == "Afternoon")

oolong_2 <- latest_data$tea_type == "Oolong"
morning_oolong <- sum(latest_data$morning_or_afternoon[oolong_2] == "Morning")
afternoon_oolong <- sum(latest_data$morning_or_afternoon[oolong_2] == "Afternoon")

organic_2 <- latest_data$tea_type == "Organic"
morning_organic <- sum(latest_data$morning_or_afternoon[organic_2] == "Morning")
afternoon_organic <- sum(latest_data$morning_or_afternoon[organic_2] == "Afternoon")

decaf_2 <- latest_data$tea_type == "Decaffeinated"
morning_decaf <- sum(latest_data$morning_or_afternoon[decaf_2] == "Morning")
afternoon_decaf <- sum(latest_data$morning_or_afternoon[decaf_2] == "Afternoon")

artisan_2 <- latest_data$tea_type == "Artisan"
morning_artisan <- sum(latest_data$morning_or_afternoon[artisan_2] == "Morning")
afternoon_artisan <- sum(latest_data$morning_or_afternoon[artisan_2] == "Afternoon")
```

Overall, `r tea_orders` customers out of `r cumulative` customers ordered tea.

`r traditional_black` customers ordered **traditional black tea**, where `r morning_black` customers ordered it in the morning and `r afternoon_black` customers ordered it in the afternoon.

`r flavoured_black` customers ordered **flavoured black tea**, where `r morning_black2` customers ordered it in the morning and `r afternoon_black2` customers ordered it in the afternoon.

`r earl_grey` customers ordered **earl grey tea**, where `r morning_earl_grey2` customers ordered it in the morning and `r afternoon_earl_grey2` customers ordered it in the afternoon.

`r traditional_green` customers ordered **traditional green tea**, where `r morning_green` customers ordered it in the morning and `r afternoon_green` customers ordered it in the afternoon.

`r flavoured_green` customers ordered **flavoured green tea**, where `r morning_green2` customers ordered it in the morning and `r afternoon_green2` customers ordered it in the afternoon.

`r herbal` customers ordered **herbal tea**, where `r morning_herbal` customers ordered it in the morning and `r afternoon_herbal` customers ordered it in the afternoon.

`r fruit` customers ordered **fruit tea**, where `r morning_fruit` customers ordered it in the morning and `r afternoon_fruit` customers ordered it in the afternoon.

`r white` customers ordered **white tea**, where `r morning_white` customers ordered it in the morning and `r afternoon_white` customers ordered it in the afternoon.

`r oolong` customers ordered **oolong tea**, where `r morning_oolong` customers ordered it in the morning and `r afternoon_oolong` customers ordered it in the afternoon.

`r organic` customers ordered **organic tea**, where `r morning_organic` customers ordered it in the morning and `r afternoon_organic` customers ordered it in the afternoon.

`r decaf` customers ordered **decaf tea**, where `r morning_decaf` customers ordered it in the morning and `r afternoon_decaf` customers ordered it in the afternoon.

`r artisan` customers ordered **artisan tea**, where `r morning_artisan` customers ordered it in the morning and `r afternoon_artisan` customers ordered it in the afternoon.
